Invaded vs non invaded

### 2015-12-05 code/08_invaded_vs_non-invaded.Rmd
save info about the networks

inv <- dplyr::data_frame(net_name = unique(node_redundancy$net) %>% as.character(),
												 inv = grepl("2", net_name) | grepl("4", net_name)) %>% 
	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))
```

>>>>

inv <- dplyr::data_frame(net_name = unique(node_redundancy$net) %>% as.character(),
												 inv = grepl("2", net_name) | grepl("4", net_name)) %>% 
	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))

inv <- plyr::ldply(net, function(x){
	data.frame(n_pla = sum(igraph::V(x)$type == "pla"),
						 n_pol = sum(igraph::V(x)$type == "pol"))
}) %>% dplyr::add_rownames() %>%
	dplyr::rename(net = rowname, 
								net_name = .id) %>% dplyr::full_join(inv)
```

Save ntw metadata
```{r}
write.csv(inv, "./data/ntw_info.csv", row.names = F)
```
